The effect of restricted substrate diffusion on microbial community function and structure

### 2019-04-17 SI_code.Rmd
MEND model changed

>>>>

```{r}
#read the data
picina<-read.xlsx(xlsxFile = c("C:/Users/cape159/Documents/pracovni/data_statistika/kopackuv_grant/michaci_pokus/DB_theory/Hasan_picek/hasan_picek12.xlsx"))

picina_monod<-monod_ex(picina)
picina_mend<-mend_ex(picina)
picina_deb<-deb_ex(picina)

picina_monod$fit$Gfit
picina_mend$fit$Gfit
picina_deb$fit$Gfit
```

```{r}

#Define the time
t_ex<-seq(0, 72)

#Define monod model
monodf<-function(time, state, pars){
      with(as.list(c(state, pars)),{
        dCb<--k*Cb+CUE*Vmax*Cb*C/(Km+C)
        dC<-k*Cb-Vmax*Cb*C/(Km+C)
        return(list(c(dCb, dC), r=(1-CUE)*Vmax*Cb*C/(Km+C), Cmic=kec*Cb))
        })
}

#Define initial conditions
Cmicinit=93.6
Cinit=315

#Use estimated parameters
monodf_pars<-picina_monod$pars

#Do the simulation
monod_sim<-as.data.frame(ode(y=c(Cb=Cmicinit/monodf_pars[["kec"]], C=Cinit), 
                                  parms=monodf_pars, monodf, times=t_ex))

######################################################################################
#Define MEND model
mendf<-function(time, state, pars){
      with(as.list(c(state, pars)),{
        dCb<--mr*Cb+CUE*Vmax*Cb*C/(Km+C)
        dC<--Vmax*Cb*C/(Km+C)
        return(list(c(dCb, dC), r=(1-CUE)*Vmax*Cb*C/(Km+C)+mr*Cb, Cmic=kec*Cb))
        })
}

#Use estimated parameters
mendf_pars<-picina_mend$pars

#Do the simulation
mend_sim<-as.data.frame(ode(y=c(Cb=Cmicinit/mendf_pars[["kec"]], C=Cinit), 
                                  parms=mendf_pars, mendf, times=t_ex))

#########################################################################################
#Define DEB model
debf<-function(time, state, pars){
      with(as.list(c(state, pars)),{
      #C uptake
      Cu=Vmax*S*C/(Km+C)
      #udrzovani
      m=S*m0
      #mobilizace rezerv
      an=f*R-m
      #respirace
      r=m+pmax(an*(1-Yu), 0)
      #microbialni uhlik je neco z rezerv a neco ze struktur
      Cmic=fr*R+fs*S
      dR<-Cu-f*R
      dS<-pmax(an*Yu,0)+pmin(0, an)
      dC<--Cu
      return(list(c(dR, dS, dC), Cmic=Cmic, r=r))
      })
}

#Use estimated parameters
debf_pars<-picina_deb$pars

#Do the simulation
deb_sim<-as.data.frame(ode(y=c(R=debf_pars[["Rinit"]], 
                               S=(Cmicinit-debf_pars[["Rinit"]]*debf_pars[["fr"]])/debf_pars[["fs"]], 
                               C=Cinit),
                           parms=debf_pars, debf, times=t_ex))

###################################################################
#Combine data
sim_all<-rbind(monod_sim[,c("time", "Cmic", "r")],
               mend_sim[,c("time", "Cmic", "r")],
               deb_sim[,c("time", "Cmic", "r")])

sim_all$Model<-c(rep("Monod", times=73), rep("MEND", times=73), rep("DEB", times=73))
sim_all$Conversion<-numeric(length = 219)
sim_all[sim_all$Model=="Monod", "Conversion"]<-picina_monod$pars[["kec"]]
sim_all[sim_all$Model=="MEND", "Conversion"]<-picina_mend$pars[["kec"]]
sim_all[sim_all$Model=="DEB", "Conversion"]<-with(deb_sim, Cmic/(R+S))

#Cmic
lbcmic_monod<-paste("R^2 == ", round(as.numeric(picina_monod$fit$Gfit[2,5]), 2))
lbcmic_mend<-paste("R^2 == ", round(as.numeric(picina_mend$fit$Gfit[2,5]), 2))
lbcmic_deb<-paste("R^2 == ", round(as.numeric(picina_deb$fit$Gfit[2,5]), 2))

#r
lbr_monod<-paste("R^2 == ", round(as.numeric(picina_monod$fit$Gfit[3,5]), 2))
lbr_mend<-paste("R^2 == ", round(as.numeric(picina_mend$fit$Gfit[3,5]), 2))
lbr_deb<-paste("R^2 == ", round(as.numeric(picina_deb$fit$Gfit[3,5]), 2))

sim1<-ggplot(picina, aes(time, Cmic))+geom_point(cex=6, pch=21, fill="grey")+
  geom_line(data=sim_all, aes(time, Cmic, linetype=Model), lwd=1.5)+theme_min+
  xlab("Time (h)")+
  ylab(expression(paste("Chloroform labile C (", mu, "g ", g^{-1}, ")")))+
  theme(legend.title = element_blank(),
        legend.position = c(0.65,0.2))+
  annotate("text", x=66, y=103.5, label=lbcmic_deb, parse=T, size=5.5)+
  annotate("text", x=66, y=99, label=lbcmic_mend, parse=T, size=5.5)+
  annotate("text", x=66, y=94.5, label=lbcmic_monod, parse=T, size=5.5)+
  ggtitle("a)")

sim2<-ggplot(picina, aes(time, r))+geom_point(cex=6, pch=21, fill="grey")+
  geom_line(data=sim_all, aes(time, r, linetype=Model), lwd=1.5)+theme_min+
  xlab("Time (h)")+
  ylab(expression(paste("Respiration rate (", mu, "g ", g^{-1}~h^{-1}, ")")))+
  theme(legend.title = element_blank(),
        legend.position = c(0.65,0.7))+
  annotate("text", x=66, y=3.35, label=lbr_deb, parse=T, size=5.5)+
  annotate("text", x=66, y=3.1, label=lbr_mend, parse=T, size=5.5)+
  annotate("text", x=66, y=2.8, label=lbr_monod, parse=T, size=5.5)+
  ggtitle("b)")

sim3<-ggplot(sim_all, aes(time, Conversion))+geom_line(aes(linetype=Model), lwd=1.5, show.legend = F)+
  theme_min+ylim(0.18, 0.25)+
  xlab("Time (h)")+
  ylab("Conversion factor")+
  theme(legend.title = element_blank(),
        legend.position = c(0.8,0.55))+
  ggtitle("c)")

grid.arrange(sim1, sim2, sim3, nrow=1)
